Cloud Supercomputing

### 2019-04-03 writing/paper/paper.tex
Added some comments. Fixed some typos

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\subsection{The ExaHyPE-Engine}
The ExaHyPE project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on expected exascale high performance computing architectures.
A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s.
The actual numerical scheme, domain decomposition and parallelisation techniques are left as black box to the user.
Internally the ExaHyPE-Engine implements a high order ADER-DG scheme on Legendre basis nodes \todo{LR: ref}.
The mesh is incorporated from the the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
The framework provides a distributed (\mpi{}) and shared memory (Intel \textsc{tbb}) parallelization tailored to dynamic adaptive mesh refinement (\amr{})~\todo{LR: ref}.
As the ADER-DG scheme is highly volatile as soon as shocks develop we additionally provide \textit{a posteriori} finite volume limiting, recently developed by \citeauthor{dumbser2016simple} in~\cite{dumbser2016simple}.
We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop} which describes our communication-avoiding implementation of the whole numerical scheme.
\newcommand{\diffCoeff}{\varepsilon}
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
    \Qj \QZZ
  \end{pmatrix}
}
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
     0\\
   \end{pmatrix}
}%
We \todo{LR: General introduction is missing. Where do we see our paper, what has been done before? Here we should also introduce and describe the ExaHyPE-Engine as base of the paper} solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]\\
    \source[\QZ]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
with vector of conserved quantitites $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
The conserved quantities
\begin{equation} 
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$ \todo{TODO: Reference to Dumbser is missing -> What are we doing differently?}.
In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.

@@

In the rest of the paper, we make the following contributions:
\begin{itemize}
\item We present an efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set.
\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item We evaluate our implementation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
\end{itemize}

>>>>

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
\section{Introduction}
\subsection{The ExaHyPE-Engine}
The ExaHyPE project (\url{www.exahype.eu}) develops an engine to solve arbitrary hyperbolic partial differential equations (\pde{}s) on expected exascale high performance computing architectures.
A user of the engine is provided with a simple code interface which mirrors the parts required to formulate a well posed Cauchy problem for a system of hyperbolic \pde{}s of first order.
The actual numerical scheme, domain decomposition and parallelisation techniques are left as black box to the user.
Internally the ExaHyPE-Engine implements a high order ADER-DG scheme on Legendre basis nodes.
The mesh is incorporated from the Peano framework~\cite{weinzierl2011}, which is based on spacetrees for Cartesian meshes.
The framework provides a distributed (\mpi{}) and shared memory (Intel \textsc{tbb}) parallelization tailored to dynamic adaptive mesh refinement (\amr{})~\todo{LR: ref}.
As the ADER-DG scheme is highly volatile as soon as shocks develop we additionally provide \textit{a posteriori} finite volume limiting, recently developed by \citeauthor{dumbser2016simple} in~\cite{dumbser2016simple}.
We want to emphasize the recent work~\cite{charrier2018stop} by \citeauthor{charrier2018stop} which describes our communication-avoiding implementation of the whole numerical scheme.
\newcommand{\diffCoeff}{\varepsilon}
\newcommand{\hyperFluxDef}{
  \begin{pmatrix}
    \Qj \\
    \Qv  \otimes \Qj + \bm{I} \pressure  \\
    \Qv \cdot (\bm{I} \QE + \bm{I} \pressure) \\
    \Qj \QZZ
  \end{pmatrix}
}
\newcommand{\viscFluxDef}{
  \begin{pmatrix}
    0\\
     \stressT (\Q, \gradQ)  \\
     \Qv \cdot \stressT (\Q, \gradQ) - \kappa \gradient{T}\\
     0\\
   \end{pmatrix}
}%
We \todo{LR: General introduction is missing. Where do we see our paper, what has been done before? Here we should also introduce and describe the ExaHyPE-Engine as base of the paper} solve the reactive compressible Navier-Stokes equations in the conservative form% \pcref{eq:conservation-law-gradient}
\begin{equation}
 \label{eq:equation-set} 
%  \begin{array}{l}
%  \text{mass cons.} \\
%  \text{momentum cons.} \\
%  \text{energy cons.} \\
%  \text{cont.\ gas} 
% \end{array}
% :
\quad
  \pdv{}{t}
  \underbrace{
  \begin{pmatrix}
    \Qrho\\
    \Qj\\
    \QE\\
    \QZ
    \end{pmatrix}}_{\Q}
  +
  \divergence{
  \underbrace{
  \left(
   \underbrace{\hyperFluxDef}_{\hyperFlux(\Q)}
+
\underbrace{\viscFluxDef}_{\viscFlux(\Q, \gradQ)}
  \right)}_{\flux(\Q, \gradQ)}}
 =
  \underbrace{
  \begin{pmatrix}
    \source[\Qrho\phantom{\Qrho}]\\
    \source[\Qj]\\
    \source[\QE]\\
    \source[\QZ]
    \end{pmatrix}}_{\source(\Q, \bm{x}, t)}
\end{equation}
with vector of conserved quantitites $\Q$, flux $\flux(\Q, \gradQ)$ and source $\source(\Q)$.
The conserved quantities
\begin{equation} 
  \label{eq:conserved-variables}
 \Q = \left( \Qrho, \Qj, \QE, \QZ \right),
\end{equation}
are the density $\Qrho$, the two or three-dimensional momentum $\Qj$, the energy density $\QE$ and the mass fraction of the chemical reactant $\QZ$.
In \cref{eq:equation-set}, the rows are the conservation of mass, the conservation of momentum, the conservation of energy and the continuity equation of the reactant.

@@

In the rest of the paper, we make the following contributions:
\begin{itemize}
\item We present an efficient, explicit \aderdg{}-scheme with shared and distributed memory parallelization for our equation set \todo{LR: das ist kein Beitrag von uns}.
\item We show an \textsc{amr}-criterion that is based on the detection of outlier cells w.r.t.\ their total variation.
\item We evaluate our implementation with standard \textsc{cfd} scenarios, atmospheric and reactive flows.
\end{itemize}
